Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-12-05 paper.tex
Spell checking (also halos -> haloes)

% Abstract of the paper
\begin{abstract}
The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe. To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined. One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, that destroys \hh{}, a necessary coolant in the creation of Pop III stars. Self-shielding can alleviate the effect the LW background has on the \hh{} within halos. In this work, we perform a cosmological simulation to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \textsc{Enzo}. We investigate the distribution of host halo masses and its relationship to the LW background intensity. Compared to previous work, halos form Pop III stars at much lower masses, up to a factor of a few, due to the inclusion of \hh{} self-shielding. We see no relationship between the LW intensity and host halo mass. Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation. Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common. 
\end{abstract}{}

@@

Once a halo becomes chemically enriched by the death of Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance. These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and can survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, delaying Pop III star formation. Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihalos. This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding. Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars. Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}. X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.

Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos. But in which halos do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars. \citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15. In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time. \citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars. They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars. This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They fit a simple analytic expression for the mass threshold of halos given a particular LW intensity $J_{\rm LW}$:
\begin{equation} \label{mthresh}
	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{0.47} .
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also found that cooling is inefficient in halos with a LW background > 0.01 $J_{\rm 21}$, where $J_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 $J_{21}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. \citet{OShea08} also found that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background \textbf{at the instance of star formation}, augmenting results from prior work. We aim to provide further insight into the host halos of Pop III stars. In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding are described. In \S 3 we present the results of our analysis. In \S 4 we discuss the results in more detail and compare with previous work. In \S 5 we conclude our discussion with a summary of our results and the implications therein.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior. The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.

@@

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, $x \equiv N_{\rm H2}/5 \times 10^{14}$ cm$^{-2}$, $b_{5} \equiv b/10^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding. \citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo. This method takes into account the Doppler-shifting of spectral lines, which can affect \hh{} shielding. With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures near $10^4$~K than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures. In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive and contain gas at lower temperatures. Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.

@@

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift, and for a given \hh{} fraction halo profile. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at $z = 24.1$ from \citet{OShea08} (their Figure 13d) with $J_{21} = 0$, which was extracted directly from their plot. These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc}. 
As the halo masses increase, the shielding factor \textbf{decreases}, meaning there is \textbf{more} shielding occurring within that halo. This behavior occurs \textbf{because as halo masses increase, more \hh{} is being added to the calculation of the column density. The more \hh{} present within a halo, the smaller the shielding factor will become}. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. Self-shielding will then significantly decrease the dissociation rate of \hh{} in the halo core, allowing for the presence of a significant \hh{} fraction even in a strong LW background.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}. These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of $J_{21}$,} and temperature projections of the box at certain points in time.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/hmf.pdf}
    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3. The thick, black line is the analytic Sheth-Tormen mass function. The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles. The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}
    \label{fig:hmf}
\end{figure}

@@

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally. The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.  There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.  Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.  Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount. We also take the center and virial radius from the \rockstar{} halo catalog. About 1\% of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}).

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by a cross, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at $<10^{6}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass steadily rises above $3 \times 10^{6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to cool at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts.

Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in Figure \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot}\ yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} \ yr^{-1}$ at $z=9.5$ (500~Myr). This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus time. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.9 and 84.1 percentiles. The right hand side shows the percentage of halos that fall below the M01 mass threshold as a function of redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $\approx$ 380 Myr, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}

>>>>

% Abstract of the paper
\begin{abstract}
The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe. To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined. One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, that destroys \hh{}, a necessary coolant in the creation of Pop III stars. Self-shielding can alleviate the effect the LW background has on the \hh{} within haloes. In this work, we perform a cosmological simulation to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \textsc{Enzo}. We investigate the distribution of host halo masses and its relationship to the LW background intensity. Compared to previous work, haloes form Pop III stars at much lower masses, up to a factor of a few, due to the inclusion of \hh{} self-shielding. We see no relationship between the LW intensity and host halo mass. Most haloes form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation. Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common. 
\end{abstract}{}

@@

Once a halo becomes chemically enriched by the death of Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these haloes is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within haloes can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in haloes, but with an increased metal abundance. These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and can survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, delaying Pop III star formation. Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihaloes. This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding. Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars. Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of haloes \citep{Yoshida03, Fernandez14}. X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.

Given the paradigm of hierarchical structure formation, haloes grow through smooth accretion and successive mergers of smaller haloes. But in which haloes do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which haloes can host Pop III stars. \citet{Tegmark97} discovered that haloes can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15. In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  haloes can cool in a Hubble time. \citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars. They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars. This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass haloes. They fit a simple analytic expression for the mass threshold of haloes given a particular LW intensity $J_{\rm LW}$:
\begin{equation} \label{mthresh}
	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{0.47} .
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also found that cooling is inefficient in haloes with a LW background > 0.01 $J_{\rm 21}$, where $J_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, haloes are able to cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 $J_{21}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. \citet{OShea08} also found that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background \textbf{at the instance of star formation}, augmenting results from prior work. We aim to provide further insight into the host haloes of Pop III stars. In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding are described. In \S 3 we present the results of our analysis. In \S 4 we discuss the results in more detail and compare with previous work. In \S 5 we conclude our discussion with a summary of our results and the implications therein.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter particle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior. The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.

@@

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, $x \equiv N_{\rm H2}/5 \times 10^{14}$ cm$^{-2}$, $b_{5} \equiv b/10^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding. \citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo. This method takes into account the Doppler-shifting of spectral lines, which can affect \hh{} shielding. With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures near $10^4$~K than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures. In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our haloes are less massive and contain gas at lower temperatures. Our calculation of the shielding factor is still valid for the temperature range of our haloes, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.

@@

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift, and for a given \hh{} fraction halo profile. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at $z = 24.1$ from \citet{OShea08} (their Figure 13d) with $J_{21} = 0$, which was extracted directly from their plot. These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc}. 
As the halo masses increase, the shielding factor \textbf{decreases}, meaning there is \textbf{more} shielding occurring within that halo. This behavior occurs \textbf{because as halo masses increase, more \hh{} is being added to the calculation of the column density. The more \hh{} present within a halo, the smaller the shielding factor will become}. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these haloes is almost at a maximum. Self-shielding will then significantly decrease the dissociation rate of \hh{} in the halo core, allowing for the presence of a significant \hh{} fraction even in a strong LW background.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ haloes that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. When the first Pop III star forms in our simulation at $z = 27$, there are only 6 haloes that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}. These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, haloes form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of $J_{21}$,} and temperature projections of the box at certain points in time.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/hmf.pdf}
    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3. The thick, black line is the analytic Sheth-Tormen mass function. The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where haloes are captured by 50 particles. The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}
    \label{fig:hmf}
\end{figure}

@@

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host haloes of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, an algorithm that adaptively refines haloes found with a friends-of-friends method in position and velocity phase-space and also temporally. The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the haloes, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. For stars that form in subhaloes identified by \rockstar{}, we assign the parent halo mass as the host halo mass.  There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.  Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.  Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount. We also take the center and virial radius from the \rockstar{} halo catalog. About 1\% of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed haloes, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}).

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by a cross, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at $<10^{6}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass steadily rises above $3 \times 10^{6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for haloes to cool at much lower masses, and therefore, Pop III stars are forming in these haloes at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts.

Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass haloes collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in Figure \ref{fig:mean_mass}, nearly 100\% of the haloes hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot}\ yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} \ yr^{-1}$ at $z=9.5$ (500~Myr). This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For haloes hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus time. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.9 and 84.1 percentiles. The right hand side shows the percentage of haloes that fall below the M01 mass threshold as a function of redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all haloes fall below the M01 relation, until $\approx$ 380 Myr, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}
